Expectations, Outcomes, and Challenges \\ of Modern Code Review

### 2013-01-10 reviews.tex
revised review 1

The results rather confirm what can be expected but are not really
surprising in my view. It is known already that code reviewing helps
finding defects, maintaining team awareness, improving code quality, and
transferring knowledge among team members. The recommendations and
implications summarize the detailed results but are also rather
high-level. While interesting I doubt that a lot can be learned.

Regarding threats to validity I agree with the authors that empirical
research done in one company can contribute to scientific development if
it is based on careful observation. However, the study might be biased
by the CodeFlow code review tool that was used by developers participating
in the study. The authors briefly discuss this issue but this discussion
should be extended in my view. Furthermore, only 17 users participated
in the study. The authors write that they sampled across different
product teams to address different perspectives and to cover different
levels of experience. Still 17 participants is not a high number given that
the CodeFlow user base is 28.000 according to the authors.

The authors investigate ad-hoc review processes. However, I missed a
discussion in the paper of how the results relate to more conventional
techniques traditionally used in code reviews. For instance, would
checklists or reading techniques be useful in the described development
context?

The paper lists a number of existing studies and papers on software
inspection and code reviews but also misses important papers from the
literature. The following references should be considered:

>>>>

\hl{The results} rather confirm what can be expected but \hl{are not really
surprising in my view}. It is known already that code reviewing helps
finding defects, maintaining team awareness, improving code quality, and
transferring knowledge among team members. \hl{The recommendations and
implications summarize the detailed results but are also rather
high-level}. While interesting I doubt that a lot can be learned.

Regarding threats to validity I agree with the authors that empirical
research done in one company can contribute to scientific development if
it is based on careful observation. However, \hl{the study might be biased
by the CodeFlow code review tool} that was used by developers participating
in the study. The authors briefly discuss this issue but this discussion
should be extended in my view. Furthermore, only 17 users participated
in the study. The authors write that they sampled across different
product teams to address different perspectives and to cover different
levels of experience. Still \hl{17 participants is not a high number} given that
the CodeFlow user base is 28.000 according to the authors.

The authors investigate ad-hoc review processes. However, \hl{I missed a
discussion in the paper of how the results relate to more conventional
techniques traditionally used in code reviews}. For instance, would
checklists or reading techniques be useful in the described development
context?

The paper lists a number of existing studies and papers on software
inspection and code reviews but also \hl{misses important papers from the
literature}. The following references should be considered:
